Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-17 chi2012.tex
Minor fixes

Heterogeneity was measured through \emph{pairwise consistency metrics} we derived from definitions in \cite{george2005understanding} and feature-metrics used in statistical instance alignment algorithms (such as summarised in \cite{bhattacharya2007collective}). Such metrics were chosen because they reflected the differences among data feeds at multiple levels -  the terminological (use of names/labels), structural, and modelling levels. Each such metric listed above is the result of averaging the pairwise score between sources in each category, separately and defined as follows:

@@

We used three metris to measure of task performance: time to completion, the number of factors used in the choice, and the number of candidates

\subsubsection{Efficiency: Time taken}
Participants spent an average of 8.9 minutes performing the tasks overall, with DP (condition A) taking slightly less time ($M=8.7$min, $SD=1.79$) per trial than condition B (the web browser/Excel interface) ($M=9.0$min; $SD=1.44$).  An ANOVA test of time taken by interface condition blocking by participant did not find a interface use a significant predictor of task completion time. A comparison of times taken are visible in Figure \ref{fig:time}.

Although across trials, restaurant selection task took on average slightly less time ($M=8.8$min,$SD=1.58$) than the university trials ($M=8.9$min,$SD=1.66$), the aforementioned ANOVA test found task type to not be a significant predictor either.

\subsubsection{Thoroughness: Factors weighed in final choice}
A second metric was the number of factors the participant considered in making their final choice. To determine this, we asked participants to tell us precisely why their choice was made, and matched their justifications to properties in the data.  This analysis revealed a significant effect of interface on number of factors weighed ($F(1,19)=3.95; p<0.10$); participants in the DP condition listed an average of 5.5 choices in their decision ($SD=1.7$) versus 4 ($SD=1.73$) in the standard condition.

\subsubsection{Diversity: Data sources consulted}
A third metric we used to gauge how well the participant performed their tasks is the number of different data sources the participant consulted during the trial. In this metric, participants used an average of 88\% of data sources provided in the DP case, compared to 80\% in the standard interface, although an ANOVA test blocking on participant demonstrated that interface choice only approached significance in predicting the number of sources consulted ($F(1,19)=0.04$ $p\approx0.10$).

\subsubsection{Effort: External cognition}
Although we did not have an explicit measure of effort for this experiment (such as NASA's TLX \cite{tlx}) the use of paper notes provided an indicator of how much participants had to keep track of during the study.  We found that participants took notes less on average (25\%) with the DP interface than the standard interface (35\%), a difference which approached significance in an ANOVA blocked by participant ($F(1,19)= 8.22; p\approx0.10$).

\subsection{Condition A (DP)}
In the A condition, where participants used DataPalette to complete their tasks they used it to collate the data on-screen, and compare multiple values directly. About half of the observed users actually used the instance combination feature of DataPalette, with the other half able to successfully make decisions without using it. Those who tried to use it were largely successful, and were able to therefore use the global brush-highlighting to simultaneously compare different statistics. Most users instantly opened up all data sources into individual boxes, in order to determine which sources contained specific statistics. The result of this technique is that the users instantly filled their screen, and ran out of space for plots and maps.

>>>>

Heterogeneity was measured through \emph{pairwise consistency metrics} we derived from definitions in \cite{george2005understanding} and feature-metrics used in statistical instance alignment algorithms (such as summarised in \cite{bhattacharya2007collective}). Such metrics were chosen because they reflected, the differences among the data feeds at multiple levels - from the simple (labelling) differneces to differences in how data was structured, and modelled. Each such metric listed above is the result of averaging the pairwise score between sources in each category, separately and defined as follows:

@@

We used three metrics to measure task performance: time to completion; the number of factors used in the choice; and the number of candidates evaluated.

\subsubsection{Efficiency: Time taken}
Participants spent an average of 8.9 minutes performing the tasks overall, with condition A (DataPalette) taking slightly less time ($M=8.7$min, $SD=1.79$) per trial than condition B (the web browser/Excel interface) ($M=9.0$min; $SD=1.44$).  An ANOVA test of time taken by interface condition blocking by participant did not find interface use a significant predictor of task completion time. A comparison of times taken are visible in Figure \ref{fig:time}.

Although across trials, the restaurant selection task took on average slightly less time ($M=8.8$min,$SD=1.58$) than the university trials ($M=8.9$min,$SD=1.66$), the aforementioned ANOVA test found task type to not be a significant predictor.

\subsubsection{Thoroughness: Factors weighed in final choice}
The second metric was the number of factors the participant considered in making their final choice. To determine this, we asked participants to tell us precisely why their choice was made, and matched their justifications to properties in the data.  This analysis revealed a significant effect of interface on number of factors weighed ($F(1,19)=3.95, p<0.10$); participants in the DP condition listed an average of 5.5 choices in their decision ($SD=1.7$) versus 4 ($SD=1.73$) in the standard condition.

\subsubsection{Diversity: Data sources consulted}
The third metric we used to gauge how well the participant performed their tasks is the number of different data sources the participant consulted during the trial. In this metric, participants used an average of 88\% of data sources provided in the DP case, compared to 80\% in the standard interface, although an ANOVA test blocking on participant demonstrated that interface choice only approached significance in predicting the number of sources consulted ($F(1,19)=0.04  p\approx0.10$).

\subsubsection{Effort: External cognition}
Although we did not have an explicit measure of effort for this experiment (such as NASA's TLX \cite{tlx}) the use of paper notes provided an indicator of how much participants had to keep track of during the study.  We found that participants took notes less on average (25\%) with the DP interface than the standard interface (35\%), a difference which approached significance in an ANOVA blocked by participant ($F(1,19)= 8.22$, $p\approx0.10$).

\subsection{Condition A (DataPalette)}
In the A condition, where participants used DataPalette to complete their tasks, they used it to collate the data on-screen, and compare multiple values directly. About half of the observed users actually used the instance combination feature of DataPalette, with the other half able to successfully make decisions without using it. Those who tried to use it were largely successful, and were able to therefore use the global brush-highlighting to simultaneously compare different statistics. Most users instantly opened up all data sources into individual boxes, in order to determine which sources contained specific statistics. The result of this technique is that the users instantly filled their screen, and ran out of space for plots and maps.
